CLT Results

### 2022-04-06 analysis/clt_data_processing.Rmd
more data

```{r}
data_mpi <- filtered_data%>%
  group_by(subjID)%>%
  distinct(trial, .keep_all = T)%>%
  mutate(correct = ifelse(targetWord == chosenWord, 1,0))%>%
  mutate(targetWord = ifelse(targetWord == "kangoroo", "kangaroo", targetWord))%>%
  left_join(aoa)%>%
  left_join(dem)%>%
  select(-timestamp)%>%
  ungroup()%>%
  mutate(age = as.numeric(difftime(test_day, birth_day, "days"))/365.25,
         age_group = substr(age,0,1))%>%
  select(-birth_day, -test_day)%>%
  filter(!is.na(age))%>%
  ungroup()
```

@@

```{r}
bind_rows(
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 1),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 2),
  read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 3)
  )%>%
  filter(!code %in% data$subjID)#%>%
  #write_xlsx("../data/clt_reminder.xlsx")
```

@@

```{r}
data%>%
  group_by(subjID)%>%
  summarise(age = round(mean(age),2))%>%
  ggplot(aes(x = age))+
  geom_jitter(aes(y = 0),width =0, height = 0.02, pch = 1, alpha =.75)+
  geom_density()+
  #ylim(-1,1)+
  theme_minimal()
```

>>>>

```{r}
data_mpi <- filtered_data%>%
  group_by(subjID)%>%
  distinct(trial, .keep_all = T)%>%
  mutate(correct = ifelse(targetWord == chosenWord, 1,0))%>%
  mutate(targetWord = ifelse(targetWord == "kangoroo", "kangaroo", targetWord))%>%
  left_join(aoa)%>%
  left_join(dem)%>%
  select(-timestamp)%>%
  ungroup()%>%
  mutate(age = as.numeric(difftime(test_day, birth_day, "days"))/365.25,
         age_group = substr(age,0,1))%>%
  select(-birth_day, -test_day)%>%
  filter(!is.na(age))%>%
  ungroup()

# filtered_data%>%
#   filter(trial == 1)%>%
#   distinct(subjID, .keep_all = T)%>%
#   left_join(dem)%>%
#   select(subjID, sex, birth_day, test_day)%>%
#   write_xlsx("../data/clt_participation_by_date.xlsx")
```

@@

```{r}
# reminder1 <- read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 15)
# 
# bind_rows(
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 1),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 2),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 3),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 4),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 5),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 7),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 10),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 12)
#   )%>%
#   filter(!code %in% data$subjID)%>%
#   filter(!code %in% reminder1$code)%>%
#   filter(code != "RY5sK3xF")%>%
#   filter(code != "s6fdepZJ")%>%
#   write_xlsx("../data/clt_reminder2.xlsx")
```

@@

```{r}
data%>%
  group_by(subjID)%>%
  summarise(age = round(mean(age),2))%>%
  ggplot(aes(x = age))+
  geom_jitter(aes(y = 0),width =0, height = 0.02, pch = 1, alpha =.75)+
  geom_density()+
  #ylim(-1,1)+
  theme_minimal()
